\mytitile\\~

### 2019-12-02 document.tex
Picture fixes

% ****** Start of file aipsamp.tex ******
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.
%
%   See the AIP README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
% 
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aipsamp
%  2)  bibtex aipsamp
%  3)  latex  aipsamp
%  4)  latex  aipsamp
%
% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 aip,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
]{revtex4-1}

@@

	\affiliation{ 
		Russian Quantum Center, Skolkovo village, Russia
	}%
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}%

	\author{V.B. Yursa}
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}%

@@

A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity. Therefore, in the main text we avoid using the standard charge and phase operators and write down its Hamiltonian using the annihilation operator $\hat b$:
\begin{equation}
\hat{{H}}_{tr}/\hbar = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
\end{equation}
where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or the ground to first excited state, $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon. Additionally, by applying external magnetic flux $\Phi_e$ (via a control current) it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}. In our modelling, we take into account only the three lowest states of the transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).

@@

Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
\end{equation}
where $\hat H_{int} = \hbar J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms. In the following, we will also transform \eqref{Hsystem} into the frame rotating with both drives by an operator
\begin{align}
&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}\\
&\hat H_R = \hat R^{\dagger}\hat H \hat R -	 {i}\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
\end{align}
Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA:
\begin{equation}
\begin{aligned}
	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
	\hat H_{int} &\rightarrow \hbar J \left[\hat b^\dag \hat c e^{(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{-(\omega_d^1 - \omega_d^2)t}\right],\\
	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

@@

Two distinct modes of simulation were used during the modelling. The first one is for the Liouvillians that do not explicitly depend on time (stationary case). In this case, the steady state $\hat \rho_{ss}$ of the system should be calculated from the set of linear equations obtained from \eqref{eq:master}:
\begin{equation}
\partial_t \hat \rho = 0 = \mathcal{L} \hat \rho
\end{equation}
This equation is solved with the qutip's \textit{steadystate} function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}. This method is applicable when the driving of the two transmons is at the same frequency since from \eqref{eq:RWA} follows that $\hat H_{int}$ becomes time independent when $\omega_d^1 = \omega_d^2$.

The second mode is required when it is not possible to avoid the time-dependence of the Liouvillian. This is the case when the transmons have to be excited at different frequencies ($\omega_d^1 - \omega_d^2 = \delta \neq 0$). From \eqref{eq:RWA} we find that even in the doubly-rotating frame $\hat H_{int}$ is oscillating, and it is not possible to simply drop this term in RWA because this will lead to qualitatively different results. In this case, to find the steady state of the system we employ the qutip's \textit{propagator} and \textit{propagator\_steadystate} functions. The propagator is a completely positive map $\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow \hat \rho(t_1)$ describing the time evolution of the system density matrix; for \eqref{eq:master}, it is defined as
\begin{equation}
\Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
\label{eq:propagator}
\end{equation}
where $\mathcal T$ is the time-ordering superoperator. Since the Liouvillian is periodic with a period of $T = 2\pi/\delta$, it is possible to calculate the steady state as the eigenvector $\hat \rho_{ss}$ of the single-period propagator $\Lambda(T, 0)$ corresponding to its largest eigenvalue\cite{dittrich1998quantum, rivas2012open}. Upon infinite applications of $\Lambda$: 
\[
\lim_{n\to \infty} \left[\Lambda(T, 0)\right]^n \hat \rho = \Lambda(nT, 0) \hat \rho \to \hat \rho_{ss}.
\]

@@

	\centering
	\includegraphics[width=\linewidth]{main_picture}
	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}. Colour shows the real part of complex transmission  through the sample. Two transmons are aligned as in \autoref{fig:experiment}~(c) and form a symmetric picture. Experimental data contain an additional horizontal line from a parasitic resonance interacting with the readout resonator. Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; other pronounced features reproduced by the modelling are shown with numbered markers (see text for description). We also denote some of the transitions $00 - ij/n$ where $i,j$ stand for the final transmon energy levels and $/n$ is optional for an $n$-photon process.}
	\label{fig:two-tone}
\end{figure*}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{stationary}
	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour). Lines show various transition frequencies from the stationary Hamiltonian. The legend labels the transitions at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
	\label{fig:statinary_levels}
\end{figure}

@@

Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms. We confirm this by numerically diagonalizing $\hat H_{tr1}+\hat H_{tr2}+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:statinary_levels}. While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}~(a), it completely misses the Roman-numbered effects. Taking into account more energy levels for transmons does not help, and is not even necessary to reproduce the experiment, as we will show in the following.

@@

\begin{figure*}
	\includegraphics[width=.49\linewidth]{powerscan}
	\includegraphics[width=.49\linewidth]{zoom2_picture}
	\caption{Power dependence of feature II: experiment and theory. Dashed are the model curves turning to dotted when the model is not expected to be valid (see Sections \ref{sec:theory} and \ref{sec:münchhausen}); model values for $\Omega_2$ are the same for both (a) and (b): $\Omega_{2}/2\pi=$ 4.5, 11.25, 22.5 and 45 MHz. \textbf{(a)} Experiment (second cooldown; the parameters are different to those in \autoref{fig:experiment}). The power of the microwave source is increased from -20 to 0 dBm and the corresponding growth of the splitting and the widths of the spectral lines is observed. \textbf{(b)} Simulation with amplitudes of the driving $\Omega_{1,2}$ equal to the model values; other parameters as in \autoref{fig:two-tone}. Note that now colours show the population of the ground state.}
	\label{fig:zoom}
\end{figure*}

\begin{figure}
	\includegraphics[width=\linewidth]{powerscan_1d}
	\caption{Linear dependence of the splitting size on the driving voltage of the microwave source $V_{rms} = \sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 50\ \Omega}$, $\Omega_2 = V_{rms}\cdot 0.23$ MHz/mV. From Section \ref{sec:theory}, the splitting size is $\frac{2\sqrt{3}}{3} \Omega_2$.}
	\label{fig:splitting_linear}
\end{figure}

@@

\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the stationary model, it is possible to use it to find which spectral lines correspond to which transitions in the system (see \autoref{fig:statinary_levels}). In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $ij/n$ where $i,j$ denote the final transmon states after the transition from the ground state, and $/n$ is optional for an $n$-photon process. We put the labels at the points where the SAM states are nearly factorized (dispersive regime for two coupled SAAs) and thus may be easily distinguished.

@@

From \autoref{fig:statinary_levels} we conclude that avoided crossing in III is between two transitions: ${12/3}$ and ${10} - {02}$ which are of the same frequency when $\omega_1 = \omega_2+\alpha_2/2$. The latter process is discernible in \autoref{fig:statinary_levels} as it depopulates ${10}$, but is not visible in \autoref{fig:two-tone}. In II, the reversed is true: ${21/3}$ and ${01} - {20}$ are crossing when $\omega_2 = \omega_1+\alpha_1/2$. From additional measurements and simulations, we have found that the size of these anticrossings depends on the driving power; the experimental and simulated results for II are shown in \autoref{fig:zoom}~(a), (b). As one can see, the growth of the splitting with increasing power is linear: its width is roughly equal to the FWHM of the ${01}$ spectral line which is approximately $\Omega_2/2\pi$ Hz. To fully quantify the shape of this splitting, in Section \ref{sec:theory} we derive analytical expressions for the dashed curves fitting the spectral lines in \autoref{fig:zoom}. By measuring the dependence of the splitting size on the microwave power we confirm its proportionality to the signal amplitude (see \autoref{fig:splitting_linear}).

@@

\paragraph{Secondary features.} Using \autoref{fig:statinary_levels}, we can get an insight into the features 1 -- 5 as well.

@@

Feature 4 is also explained by the stationary model and is caused by several spectral lines and a pair of avoided crossings near a single point (dotted lines in \autoref{fig:statinary_levels}). It appears at the point where ${02/2}$ intersects ${20/2}$ and is just barely visible in the experimental data because of the noise. Feature 5 is located at the intersection between ${20/2}$ and normally invisible ${10} - {02}$, and can be found in the experimental data, too.

@@

Now, we will repeat this reasoning using a quantitative mathematical model. We start from the initial Hamiltonian \eqref{Hsystem}. To move to the rotating frame with \eqref{eq:rotation} and apply the RWA, will use the following operator:
\begin{equation}
R = \exp[-i\omega_d^1 t (b^{\dagger}b+c^{\dagger}c)]
\end{equation}  
Note that we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$:
\begin{equation}
\begin{aligned}
\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{1},\\
\hat H_{int} &\rightarrow  \hbar J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2} \hat \sigma_x,\ 
\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
\end{aligned}
\end{equation}
where $\delta = \omega_{d}^2 - \omega_{d}^1$.

Since $\hat H_{d}^1$ is now time-independent, we can move to the dressed basis by applying a transformation $\hat S$ which diagonalizes the first transmon. After that, the Hamiltonian may be split into three parts:
\begin{equation}
\begin{aligned}
\hat H^{D} &= \left[\frac{\Delta_1}{2} \hat{\mathbbm{1}}+\frac{\Omega_1^R}{2}\hat \sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b +\frac{1}{2}\alpha_2 \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),\\
\hat V_J &= \hat S^\dag \hat H_{int}\hat S,\\
\hat V_t &= \hat S^\dag \hat H_{d}^{2} \hat S \equiv \hat H_{d}^{2}.
\end{aligned}
\end{equation}
The first part is diagonal, and the remaining two will be treated as perturbations. To simplify futher calculations, we take the working point where $\Delta_1 = 0$ and $\Delta_2 = - \alpha_2/2$. In these conditions, $H^D$ becomes degenerate as can be seen in \eqref{eq:ham_matrix} of Appendix \ref{sec:H_mat}.

Using the degenerate perturbation theory with $\hat V_J$ summarized in Appendix \ref{sec:dpt}, we have found the first-order corrected wave functions of $\hat H^D$, labelled $\ket{k},\ k=1..6$.

The theory for two-photon processes is given in Appendix \ref{sec:2pp}. The probability rate of two-photon transition per unit interaction time using corrected eigenstates $\ket{k}$ and neglecting small terms we obtain:

\begin{equation}
A^{(2)}_{1\rightarrow 6} = 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha + \text{$\Omega_1
		$}\right)^2}{\alpha ^{6}\Omega_1^2}
\end{equation}
\begin{equation}
A^{(2)}_{2\rightarrow 5} = 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
		$}\right)^2}{\alpha ^{6}\Omega_1^2}
\end{equation}
From here it follows that in the studied SAM the sideband transitions are prohibited without interaction $(J=0)$ even in the second order, and the avoided crossing we are interested can not be observed.

\paragraph{Feature I.} Finally, we discuss the last of the dressing effects observed in the SAM. Its explanation is illustrated in \autoref{fig:featureI} for the case when $\Omega_2 \gg \Omega_1$. In this case, the second qubit is dressed, and the splitting has the shape shown in \autoref{fig:featureI}~(a). For the opposite case, the explanation is the same. As one can see, only the two-photon transition $11/2$ is affected. When the transitions $01$ and $10$ are close resonance, its frequency is $\omega_{11/2} \approx \omega_1 \approx \omega_2$ Similarly to the previous case with II and III, in the dressed basis, this transitions becomes a single-photon doublet transition for $\hat H_d^2$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b). Note that in the experiment with only a single excitation frequency, it is not possible to observe both transitions at the same magnetic flux, and this is clearly visible in \autoref{fig:difdrive}. Instead, we observe one line to the left and the other to the right from the $01-10$ intersection. This behaviour will be explained in the following section.

@@

\paragraph{Features II, III.}As shown in \autoref{fig:main_scheme}~(d), the sideband transitions are formed by two-photon processes for $\hat H_d^2$. On the other hand, we know from the stationary solution that in the laboratory frame the two transitions forming the avoided crossing are $10 - 02$ (one-photon) and $12/3$ (three-photon). This means that there should be a smooth transformation between 1-, 2- and 3-photon processes when the system approaches the resonant point. Let's consider two-photon transitions $(10 - 02)/2$ and $12/2$. In the frame rotating with the first qubit (like in \autoref{fig:main_scheme}~(c)) when $\Omega_1$ = 0 (no driving yet on the first qubit), their frequencies are:
\begin{equation}
\begin{aligned}
\omega_{(10-02)/2} &= (\alpha_2 + 2 \omega_{2} - \Delta_1)/2,\\
 \omega_{12/2} &= (\alpha_2 + 2 \omega_{2} + \Delta_2)/2.
\end{aligned}
\end{equation}
When the first transmon becomes dressed by $\Omega_1 \neq 0$, its splitting $\Delta_1$ changes to $\Omega^R_1 =\sqrt{\Omega_{1}^2 + \left(\omega_{1} - \omega_{d}\right)^{2}}$. At this point it becomes clear that at the resonant point where $\alpha_2 + 2 \omega_{2} = 2\omega_1$, $\omega_{(10-02)/2}$ and $\omega_{12/2}$ are exactly equal to the two-photon sideband frequencies $\omega_1 \pm \Omega_1^R/2$ established above and thus should be used to model the splitting behaviour.

>>>>

% ****** Start of file aipsamp.tex ******
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.
%
%   See the AIP README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
% 
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aipsamp
%  2)  bibtex aipsamp
%  3)  latex  aipsamp
%  4)  latex  aipsamp
%
% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 pra,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
]{revtex4-1}

@@

	\affiliation{ 
		Russian Quantum Center, Skolkovo village, Russia
	}%
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}
	\affiliation{
		National University of Science and Technology MISiS, Moscow, Russia
	}%
	\author{V.B. Yursa}
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}%

@@

A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity. Therefore, in the main text we avoid using the standard charge and phase operators and write down its Hamiltonian using the annihilation operator $\hat b$:
\begin{equation}
\hat{{H}}_{tr}/\hbar = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
\end{equation}
where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or from ground to first excited state, $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon. Additionally, by applying external magnetic flux $\Phi_e$ (via a control current) it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}. In our modelling, we take into account only the three lowest states of the transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).

@@

Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
\end{equation}
where $\hat H_{int} = \hbar J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms. In the following, we will also transform \eqref{Hsystem} into the frame rotating with both drives by an operator
\begin{align}
&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}\\
&\hat H_R = \hat R^{\dagger}\hat H \hat R -	 {i}\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
\end{align}
Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA
\begin{equation}
\begin{aligned}
	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
	\hat H_{int} &\rightarrow \hbar J \left[\hat b^\dag \hat c e^{(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{-(\omega_d^1 - \omega_d^2)t}\right],\\
	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

@@

Two distinct modes of simulation were used during the modelling. The first one is for the Liouvillians that do not explicitly depend on time (stationary case). In this case, the steady state $\hat \rho_{ss}$ of the system should be calculated from the set of linear equations obtained from \eqref{eq:master}
\begin{equation}
\partial_t \hat \rho = 0 = \mathcal{L} \hat \rho
\end{equation}
This equation is solved with the qutip's \textit{steadystate} function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}. This method is applicable when the driving of the two transmons is at the same frequency since from \eqref{eq:RWA} follows that $\hat H_{int}$ becomes time independent when $\omega_d^1 = \omega_d^2$.

The second mode is required when it is not possible to avoid the time-dependence of the Liouvillian. This is the case when the transmons have to be excited at different frequencies ($\omega_d^1 - \omega_d^2 = \delta \neq 0$). From \eqref{eq:RWA} we find that even in the doubly-rotating frame $\hat H_{int}$ is oscillating, and it is not possible to simply drop this term in RWA because this will lead to qualitatively different results. In this case, to find the steady state of the system we employ the qutip's \textit{propagator} and \textit{propagator\_steadystate} functions. The propagator is a completely positive map $\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow \hat \rho(t_1)$ describing the time evolution of the system density matrix; for \eqref{eq:master}, it is defined as
\begin{equation}
\Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
\label{eq:propagator}
\end{equation}
where $\mathcal T$ is the time-ordering superoperator. Since the Liouvillian is periodic with a period of $T = 2\pi/\delta$, it is possible to calculate the steady state as the eigenvector $\hat \rho_{ss}$ of the single-period propagator $\Lambda(T, 0)$ corresponding to its largest eigenvalue\cite{dittrich1998quantum, rivas2012open}. Upon infinite applications of $\Lambda$
\[
\lim_{n\to \infty} \left[\Lambda(T, 0)\right]^n \hat \rho = \Lambda(nT, 0) \hat \rho \to \hat \rho_{ss}.
\]

@@

	\centering
	\includegraphics[width=\linewidth]{main_picture}

	\includegraphics[width=.55\linewidth]{stationary}
	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}. Colour shows the real part of complex transmission  through the sample. Two transmons are aligned as in \autoref{fig:experiment}~(c) and form a symmetric picture. Experimental data contain an additional horizontal line from a parasitic resonance interacting with the readout resonator. Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; other pronounced features reproduced by the modelling are shown with numbered markers (see text for description). We also denote some of the transitions $00 - ij/n$ where $i,j$ stand for the final transmon energy levels and $/n$ is optional for an $n$-photon process. \textbf{(c)} Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour). Lines show various transition frequencies from the stationary Hamiltonian. The legend labels the transitions at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
	\label{fig:two-tone}
\end{figure*}

@@

Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms. We confirm this by numerically diagonalizing $\hat H_{tr}^1+\hat H_{tr}^2+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:two-tone}~(c). While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}~(a), it completely misses the Roman-numbered effects. Taking into account more energy levels for transmons does not help, and is not even necessary to reproduce the experiment, as we will show in the following.

@@

\begin{figure*}
	\includegraphics[width=.49\linewidth]{powerscan}
	\includegraphics[width=.49\linewidth]{zoom2_picture}

	\includegraphics[width=.7\linewidth]{powerscan_1d}
	\caption{Power dependence of feature II: experiment and theory. Dashed are the model curves turning to dotted when the model is not expected to be valid (see Sections \ref{sec:theory} and \ref{sec:münchhausen}); model values for $\Omega_2$ are the same for both (a) and (b): $\Omega_{2}/2\pi=$ 4.5, 11.25, 22.5 and 45 MHz. \textbf{(a)} Experiment (second cooldown; the parameters are different to those in \autoref{fig:experiment}). The power of the microwave source is increased from -20 to 0 dBm and the corresponding growth of the splitting and the widths of the spectral lines is observed. \textbf{(b)} Simulation with amplitudes of the driving $\Omega_{1,2}$ equal to the model values; other parameters as in \autoref{fig:two-tone}. Note that now colours show the population of the ground state. \textbf{(c)} Linear dependence of the splitting size on the driving voltage of the microwave source $V_{rms} = \sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 50\ \Omega}$, $\Omega_2 = V_{rms}\cdot 0.23$ MHz/mV. From Section \ref{sec:theory}, the splitting size is $\frac{2\sqrt{3}}{3} \Omega_2$.}
	\label{fig:zoom}
\end{figure*}

@@

\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the stationary model, it is possible to use it to find which spectral lines correspond to which transitions in the system (see \autoref{fig:two-tone}~(c)). In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $ij/n$ where $i,j$ denote the final transmon states after the transition from the ground state, and $/n$ is optional for an $n$-photon process. We put the labels at the points where the SAM states are nearly factorized (dispersive regime for two coupled SAAs) and thus may be easily distinguished.

@@

From \autoref{fig:two-tone}~(c) we conclude that avoided crossing in III is between two transitions: ${12/3}$ and ${10} - {02}$ which are of the same frequency when $\omega_1 = \omega_2+\alpha_2/2$. The latter process is discernible in \autoref{fig:two-tone}~(c) as it depopulates ${10}$, but is not visible in \autoref{fig:two-tone}. In II, the reversed is true: ${21/3}$ and ${01} - {20}$ are crossing when $\omega_2 = \omega_1+\alpha_1/2$. From additional measurements and simulations, we have found that the size of these anticrossings depends on the driving power; the experimental and simulated results for II are shown in \autoref{fig:zoom}~(a), (b). As one can see, the growth of the splitting with increasing power is linear: its width is roughly equal to the FWHM of the ${01}$ spectral line which is approximately $\Omega_2/2\pi$ Hz. To fully quantify the shape of this splitting, in Section \ref{sec:theory} we derive analytical expressions for the dashed curves fitting the spectral lines in \autoref{fig:zoom}. By measuring the dependence of the splitting size on the microwave power we confirm its proportionality to the signal amplitude (see \autoref{fig:zoom}~(c)).

@@

\paragraph{Secondary features.} Using \autoref{fig:two-tone}~(c), we can get an insight into the features 1 -- 5 as well.

@@

Feature 4 is also explained by the stationary model and is caused by several spectral lines and a pair of avoided crossings near a single point (dotted lines in \autoref{fig:two-tone}~(c)). It appears at the point where ${02/2}$ intersects ${20/2}$ and is just barely visible in the experimental data because of the noise. Feature 5 is located at the intersection between ${20/2}$ and normally invisible ${10} - {02}$, and can be found in the experimental data, too.

@@

Now, we will repeat this reasoning using a quantitative mathematical model. We start from the initial Hamiltonian \eqref{Hsystem}. To move to the rotating frame with \eqref{eq:rotation} and apply the RWA, will use the following operator:
\begin{equation}
R = \exp[-i\omega_d^1 t (b^{\dagger}b+c^{\dagger}c)].
\end{equation}  
Note that we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$. Now,
\begin{equation}
\begin{aligned}
\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{1},\\
\hat H_{int} &\rightarrow  \hbar J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2} \hat \sigma_x,\ 
\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
\end{aligned}
\end{equation}
where $\delta = \omega_{d}^2 - \omega_{d}^1$.

Since $\hat H_{d}^1$ is now time-independent, we can move to the dressed basis by applying a transformation $\hat S$ which diagonalizes the first transmon. After that, the Hamiltonian may be split into three parts
\begin{equation}
\begin{aligned}
\hat H^{D}/\hbar &= \left[\frac{\Delta_1}{2} \hat{\mathbbm{1}}+\frac{\Omega_1^R}{2}\hat \sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b +\frac{1}{2}\alpha_2 \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),\\
\hat V_J &= \hat S^\dag \hat H_{int}\hat S,\\
\hat V_t &= \hat S^\dag \hat H_{d}^{2} \hat S \equiv \hat H_{d}^{2}.
\end{aligned}
\end{equation}
The first part is diagonal, and the remaining two will be treated as perturbations. To simplify further calculations, we consider the point where $\Delta_1 = 0$ and $\Delta_2 = - \alpha_2/2$. In these conditions, $H^D$ becomes degenerate as can be seen in \eqref{eq:ham_matrix} of Appendix \ref{sec:dpt}. Using the degenerate perturbation theory for $\hat V_J$ summarized therein, we find the first-order corrected wave functions of $\hat H^D + \hat V_J$, labelled $\ket{k},\ k=1..6$.

The time-dependent perturbation theory that we use to calculate the transition rates of the two-photon processes stimulated by $\hat V_t$ is reviewed in Appendix \ref{sec:2pp}. Using the corrected eigenstates $\ket{k}$ and neglecting small terms we obtain the following expression for the transition rates per unit time\cite{faisal2013theory}:
\begin{equation}
\begin{aligned}
R^{(2)}_{1\rightarrow 6} &= 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha + \text{$\Omega_1$}\right)^2}{\alpha ^{6}\Omega_1^2},\\
R^{(2)}_{2\rightarrow 5} &= 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
		$}\right)^2}{\alpha ^{6}\Omega_1^2}.
\end{aligned}\label{eq:rates}
\end{equation}
From \eqref{eq:rates} follows that the sideband transitions are prohibited without the interaction in the SAM $(J=0)$, and the extra avoided crossings will not be observed.

\paragraph{Feature I.} Finally, we discuss the last Roman-numbered effect. It is illustrated in \autoref{fig:featureI} for the case when $\Omega_2 \gg \Omega_1$: the second qubit is dressed, and the splitting has the shape shown in \autoref{fig:featureI}~(a). For the opposite case ($\Omega_1 \gg \Omega_2$), the logic is the same.

As one can see from \autoref{fig:difdrive}, only the two-photon transition $11/2$ is affected and experiences a frequency shift approaching the 01-10 intersection while the other spectral lines are not moving. Similarly to II and III, in the frame rotating with the second transmon it tuns into two different single-photon transitions for $\hat H_d^1$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b). We will show below that in the experiment with a single excitation frequency, it is not possible to observe both transitions simultaneously; this is clearly visible in \autoref{fig:difdrive}. Instead, we observe one line to the left and the other to the right from the $01-10$ intersection.

@@

\paragraph{Features II, III.}As shown in \autoref{fig:main_scheme}~(d), the sideband transitions are formed by two-photon processes for $\hat H_d^2$. On the other hand, we know from the stationary solution that in the laboratory frame the two transitions forming the avoided crossing are $10 - 02$ (one-photon) and $12/3$ (three-photon). This means that there should be a smooth transformation between 1-, 2- and 3-photon processes when the system approaches the resonant point. Let's consider two-photon transitions $(10 - 02)/2$ and $12/2$. In the frame rotating with the first qubit (like in \autoref{fig:main_scheme}~(c)) when $\Omega_1$ = 0 (no driving yet on the first qubit), their frequencies are
\begin{equation}
\begin{aligned}
\omega_{(10-02)/2} &= (\alpha_2 + 2 \omega_{2} - \Delta_1)/2,\\
 \omega_{12/2} &= (\alpha_2 + 2 \omega_{2} + \Delta_2)/2.
\end{aligned}
\end{equation}
When the first transmon becomes dressed by $\Omega_1 \neq 0$, its splitting $\Delta_1$ changes to $\Omega^R_1 =\sqrt{\Omega_{1}^2 + \left(\omega_{1} - \omega_{d}\right)^{2}}$. At this point it becomes clear that at the resonant point where $\alpha_2 + 2 \omega_{2} = 2\omega_1$, $\omega_{(10-02)/2}$ and $\omega_{12/2}$ are exactly equal to the two-photon sideband frequencies $\omega_1 \pm \Omega_1^R/2$ established above and thus should be used to model the splitting behaviour.
